---
title: "ChIPexoQualExample: Accompanying example data for ChIPexoQual"
author:
  - name: Rene Welch
    affiliation: &id Department of Biostatistics and Medical Informatics, University of Wisconsin-Madison
    email: rwelch2@wisc.edu
  - name: S&#252;nd&#252;z Kele&#351
    affiliation:
      - Department of Statistics, University of Wisconsin-Madison
      - *id
package: ChIPexoQualExample
date: "`r BiocStyle::doc_date()`"
bibliography: biblio.bib     
vignette: >
    %\VignetteIndexEntry{ChIPexoQualExample}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
output:
    BiocStyle::html_document    
---

```{r style, echo = FALSE, results = 'asis'}`r ''`
BiocStyle::markdown()
```

<meta http-equiv="content-type" content="text/html;charset=utf-8" />

# Overview

`r BiocStyle::Biocpkg("ChIPexoQualExample")` is an the accompanying example data package for `r BiocStyle::Biocpkg("ChIPexoQual")`. The data was built from the FoxA1 in mouse liver experiment published by [@exoillumina], by considering only the reads aligned to **chr1**. To load the package it is necessary to use:

```{r load, include=TRUE, echo=TRUE, eval=FALSE}
library(ChIPexoQualExample, quietly = TRUE)
```

This package contains these aligned reads and an example run with `r BiocStyle::Biocpkg("ChIPexoQual")`:

```{r files}
## example raw files
list.files(system.file("extdata", package = "ChIPexoQualExample"))

```


# SessionInfo

```{r info,include=TRUE,echo =TRUE,eval=TRUE}
sessionInfo()
```

# References

