---
title: "ChIPexoQualExample: Accompanying example data for ChIPexoQual"
author: |
        | Rene Welch and S&#252;nd&#252;z Kele&#351;
        | Department of Statistics, University of Wisconsin-Madison
output: 
    BiocStyle::html_document
bibliography: biblio.bib        
vignette: >
    %\VignetteIndexEntry{Vignette Title}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}  
---
    
```{r style, echo = FALSE, results = 'asis'}

    library(BiocStyle)
    markdown(css.files = c('custom.css'))

```

# Overview

`r Biocpkg("ChIPexoQualExample")` is an the accompanying example data package for `r Biocpkg("ChIPexoQual")`. The data was built from the FoxA1 in mouse liver experiment published by [@exoillumina], by considering only the reads aligned to **chr1**. To load the package it is necessary to use:

```{r muteload,include=FALSE,echo=FALSE,eval = TRUE}
    
    library(ChIPexoQual)
    library(ChIPexoQualExample)
    
```    

```{r load,include=TRUE,echo=TRUE,eval=FALSE}

    library(ChIPexoQualExample)

```

This package contains these aligned reads and an example run with `r Biocpkg("ChIPexoQual")`:

```{r example}
    
    ## example raw files
    list.files(system.file("extdata",package = "ChIPexoQualExample"))
    
    ## example run
    data("exampleExoData")
    exampleExoData[[1]]
    
```

# SessionInfo

```{r info,include=TRUE,echo =TRUE,eval=TRUE}
sessionInfo()
```

# References

